Title?

### 2019-08-21 April/paper_wc_save3.tex
On hold.

We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

@@

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in this secondary market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many ISPs each holding
thier own local auction; there is no entity that holds a global market knowledge.

@@

The paper is organized as follows...

@@

% MECHANISM
\subsection{Data Auction Mechanism}\label{mechanism}
We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the secondary market. We will denote the \emph{data} PSP rules
by including an overbar, in order to emphasize that they have been changed from
the original forms described in \cite{lazar}.
The market price function (MPF) for a buyer in the secondary market
can now be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    \bar{P}_i&(z, s_{-i}) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {\bar{D}_i^j}(y,s_{-i}^j) \ge z\bigg\rbrace \bigg),\\
\end{split}
\end{align}
and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
order to obtain
data amount $z$ given an opponent profile $s_{-i}$. We note that
the total minimum price for the buyer must be an aggragation of the
\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
%buyer $i$'s bid quantity. 
The maximum available quantity of data from seller
$j$ at price $y$ given $s_{-i}$ is: 
% NEW ALLOCATION RULE
\begin{align}
\begin{split}\label{datacomposed}
    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
\end{split}
\end{align}
and we have the inverse price function as an aggragate over all local auctions
$j\in \mcI_i$,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
\bar{D}_i^j \big) : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
\end{split}
\end{align}
% DATA ALLOCATION RULE
The data allocation rule is given as in \cite{semret}, however with the
influence of the opt-out buyer strategy, the resulting allocation is a function of the total amount of data
required by buyer $i$ composed with its opt-out value and the allocation relies
on the incentives of the seller, so that $\forall \ i \in \mcI^j$,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
\begin{split}
    \bar{a}_i(s) &= a_i(s) \circ e_i =
\displaystyle\sum_{j\in\mcI_i}\bigg(\min\bigg\lbrace d_i^j,
\\
    &\frac{d_i^j}{\sum_{k:p_k^j=
p_i^j}d_k^j}
\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace\bigg).
\end{split}
\end{align}
Finally, we must have that the cost to the buyer adheres to the second price rule for each local auction:
% DATA COST
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI_i} 
p^j \bigg(\bar{a}_j(0; s_{-i}^j)
    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg).
\end{split}
\end{align}

The main contribution of this work 
is an auction mechanism inspired by the classic PSP throughput problem. In
order to apply a distributed PSP implementation to CMHK's secondary market,
we utilize our opt-out buyer and seller strategies in order to analize the
behavior of the resulting dynamical market. As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the communication
expense from numerous local auctions trading an infinitely divisible resource.
We will assume that the cost of participatingn in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. We perform a simple survey of these bid fee models, we
provide some idea of the expected revenue of the mobile data ISP (NEED
STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
market, additionally, the purchased data expires (does not carry to the next
service period). Therefore, a simple definition of market equilibrium, where
supply equals demand, is insufficent to complete a comprehensive analysis of
the CMHK data-exchange market behavior. We will make an attempt to address why
our formulation at least partially considers some of these issues (BAD), such
as the impact of the bid fee on user behavior. (MOVE SOME OF THIS UP)
Finally, we  .... (WHAT? COMPLETE THE THOUGHT)

We claim that the market is
able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, our mechanism provides the functions
for the effective communication between the connected users. It was shown in
\cite{lazar} that a $2$-dimensional message space is sufficient for the PSP
auction. Using a restricted message space is essential for the distributed
nature of our design (EXPLAIN), however, as a given message can come from many
possible types, there is no single
way to do the transformation from the direct revelation mechanism to the
desired one. This is equivalent to guessing the
right direct-revelation-to-desired-mechanism transformation and building it
into the allocation rule from the start. (FINISH!)
We claim that in
this secondary market our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead (and so possibly fees paid to the ISP)
and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
with respect to the classic throughput problem.

@@

We assume that users are selfish, and therefore
rational. Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
In general, user preferences are defined by a utility function, for any $i\in\mcI$,
\begin{align*}
    u_i : &S \rightarrow (-\infty, \infty) \\
          &s \rightarrow u_i(s).
\end{align*}

@@

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that a seller may come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that a buyer must coordinate their bids among multiple sellers. 
Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
moderated by the function $e_i$ which maps its data requirement to the distributed market. 
We propose the following strategy, 
% BUYER STRATEGY
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Define any auction duration to be $\tau \in [0,\infty)$. 
Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
$t\in\tau$. For any allocation $a$ at time $t$, let
% OPT-OUT BUYER STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
    e_i^j(a) \triangleq a_i^j,
\end{equation}
and define,
% MIN SET
$$
    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} d^j.
$$
Buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
    n = \argmin_{j\in \ell_i}(n d^j\ge d_i\rbrace,
\end{equation} 
which produces a minimal subset 
\begin{equation}\label{sellers}
    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
\end{equation} 
Now let $j^* = n \le I$, and define, 
\begin{equation}\label{opt-minallocation}
    e_i(a) \triangleq e_i^{j^*}(a).
\end{equation}

We have that $e_i$ defines an optimal feasible strategy for buyer $i$ for any
time $t\in\tau$.
}\\
\textbf{Proof:}
We assume that a buyer wants to fufill their data requirement.
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\ell_i$. If we suppose that $d_i >
\sum_{j\in\mcI}d^j$, then $j^* > I$ and $\ell_i = \emptyset$, 
we model the ISP as a seller $k$ with bid $s^k =(d^k, p^k)$, where $d^k > d^j, \
\forall \ j\in\mcI_i$, an
$p^k$ is the overage fee for data set by the ISP, which is also the upper bound of the sellers'
pricing function, and so again (\ref{buyercoordinate}) holds.
As prices are a bounded set, we consider some $k \ne i \in
\mcI$ where $p_i^j = p_k^j$. 
The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
between all buyers with the same unit price. 
This would result in a partial allocation of data to $i$ and $k$, and so neither
buyer would satisfy thier demand as expected. (NOT QUITE SURE
HOW I WANT TO HANDLE THIS YET ... WANT PROPORTIONAL SPLIT TO WORK WITH PARTIAL
DATA ALLOCATION FOR BUYERS AND SELLERS)
Additionally, we consider the transition from time $t$ to time $(t+1)$, and a
new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other words, a new buyer $k$ may enter the market with a better
price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
$n$ so that
$$
    e_i^{(t+1)}(a) = e_i^{(t)}(a) - e_k^{(t)}(a),
$$
and the subset $\mcI_i$ is large enough to balance the additional demand from
$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
and we determine that the opt-out strategy is optimal.

Finally, we note that $\mcI_i$ is not the only
possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
minimal ordered subset where a
coordinated bid is possible, the reasoning for which we will address in further analysis (Section
\ref{analysis}).

\subsubsection{Buyer Influence}
The buyer demand is a key market influence (SILLY SENTENCE), as the buyer
valuation is elastic, even infintesimal changes in the market dynamics can be
modeled. $\forall \ y\ge 0$, we determine that the demand for $j$ is given by,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
\end{equation}

Buyers are influenced by each others' behavior, each buyer has an incentive to
remain a participant in all of the auctions.
We define the ``inverse" demand for any buyer $i$,
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f_i$ maps a unit of data to the lowest price at
which $i$ \emph{could} buy the unit from \emph{any} seller $j\in\mcI$. This is the
lowest potential unit cost of the buyer, and corresponds to the maximum reserve
price amongst the sellers. 
The revenue for $j$ at unit price $y$ is also determined by the
demand of the buyers.
We define the ``inverse" of the buyer demand function for seller $j$:
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
where $f^j$ maps to the highest possible unit data price.
Thus we have the following Lemma. 
{
\lemma{(User valuation)}\label{uservaluation}
For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
\begin{equation}\label{buyerprice}
    \theta_i^j \circ e_i = \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{equation}
it follows that 
\begin{equation}\label{valuation}
    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
 \int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}
Similarly, seller $j$'s valuation is,
\begin{equation}\label{sellervaluation}
    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a buyer wants to minimize the cost of purchasing their data
requirement, at the same time ensuring they get the full allocation $e_i(a)$,
and so must minimally meet $j$'s reserve price.
A seller will try to maximize profit for any given allocation $a$,
and will try to sell all of its data, and so 
$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = b^j =
\sum_{i\in\mcI} e_i$,
The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)

The sellers' natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
We have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper.

As $j$'s behavior is restricted by
the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
{
% SELLER CONSTRAINTS
\lemma{(Seller constraints)}\label{constraints}
Let $j$ be a seller with budget $b^j$.
First, the seller must satisfy the quantity
constraint, 
\begin{equation}\label{quantity}
    d^j \ge e_i(a)
\end{equation}
and
\begin{equation}\label{budget}
    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j,
\end{equation}
which implies, for any $i\in\mcI$,
\begin{equation}\label{partialallocation}
    e_i^j(a) \le b^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
\end{equation}
In addition, for a rational seller, the reserve price must
satisfy 
\begin{equation}\label{reserveprice}
   p^j \ge \min_{i\in\mcI}\big(p_i^j).
\end{equation}
}\\
\textbf{Proof:}
The first statement is obvious, 
a seller cannot sell more data than indicated in their bid, (\ref{budget}) and
(\ref{partialallocation}) enforce
the budget constraint for the seller. Finally, (\ref{reserveprice})
follows from the assumption that $j$ is rational, and so utility-maximization
acts as revenue maximization; a rational seller will not sell its
data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)

\subsubsection{Seller Strategy}
In order to to develop the seller strategy, it is necessary we determine 
that a seller has an incentive to
accept fractional (CHANGE TO PARTIAL? PICK ONE) bids (i.e. sell a fraction of
their budget $b^j$). Reasonably,
there may not exist a buyer such that $d_i = b^j$. \cite{zheng} reasons that the seller does not know the exact amount of
leftover data available, and so they may only sell enough data to ensure that
they will not become a buyer while they submit their total data overage to the
secondary market. Buyers are allowed to
bid both dynamically and asychronously, and as a seller determines allocations using only bids
in its local market. Therefore, in order to
maximize the revenue gained per unit of data the seller must respond to the
varation of competitive bids in its market (MORE? FUTURE WORK? CITE?).

We describe the sellers' \emph{local} auction strategy for allocating its
data according to the constraints formed by the buyer strategy. As
local auction is progressive, and influenced by the $\epsilon$-best replies of
the buyers, we will need the following Lemma. 
We now define the local auction, which we describe, when coupled with the buyer
responses, as a progressive game of strategy with incomplete, but perfect
information (SAY MORE?).
(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)

>>>>

We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications providers' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

@@

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in this secondary market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many providers each holding
thier own local auction; there is no entity that holds a global market knowledge.

@@

@@

@@

We assume that users are selfish, and therefore
rational. Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
User preferences are defined by a utility function, for any $i\in\mcI$,
\begin{align*}
    u_i : &S \rightarrow (-\infty, \infty) \\
          &s \rightarrow u_i(s).
\end{align*}
(TOO GENERAL?)

@@

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that a seller may come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that a buyer must coordinate their bids among multiple sellers. 
Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
moderated by the function $e$ which maps its data requirement to the distributed market. 
We propose the following strategy,
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Let $i\in\mcI$ be a buyer and define any auction duration
to be $\tau \in [0,\infty)$, and fix all other buyers' bids $s_{-i}$. 
For any allocation $a$, let
% OPT-OUT BUYER STRATEGY
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
    e_i^j(a) \triangleq a_i^j,
\end{equation}
and define,
% MIN SET
$$
    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} d^j.
$$
Buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
    n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
\ge d_i\rbrace,
\end{equation} 
which produces a minimal subset 
\begin{equation}\label{sellers}
    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
\end{equation} 
Now let $j^* = n \le I$, and define, 
\begin{equation}\label{opt-minallocation}
    e_i(a) \triangleq e_i^{j^*}(a).
\end{equation}
we address the following special cases:\\
(Budget limited allocation)
\begin{equation}\label{partialallocation}
    d_i^j > b^j - \sum_{k\in\mcI^j, k\ne i} d_k^j.
\end{equation}
(Equal price allocation)
There exists $k,i \in \mcI^j, k\ne i$, such that
\begin{equation}\label{equalprice}
    \quad p_i^j = p_k^j.
\end{equation}
(Price-dominant allocation)
There exists $k \ni \mcI^j$, where $\forall \ i\ne k \in \mcI^j$.
\begin{equation}\label{newbuyer}
    p_k^j < p_i^j, 
    %p_i^j < p_k^j \quad \text{and} \quad d_i^j >= b^j, \quad \forall \ k \in \mcI^j.
\end{equation}
(Empty allocation)
\begin{equation}\label{emptyset}
    n > \vert \mcI\vert \Rightarrow \ell^j = \emptyset.
\end{equation}
In any of the above cases, seller $j$'s local auction strategy does not change and
Proposition \ref{sellerstrategy} holds.
Then, we have that $e_i$
is an optimal feasible strategy for buyer $i$.
}\\
\textbf{Proof:}
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\ell_i$. In the case that $d_i >
\sum_{j\in\mcI}d^j$, then $j^* > I$, we reason that this case is unlikely; our formulation reduces to a
monopoly, and the user pays the overage fee for data set by the provider which the upper bound of the sellers'
pricing function, where we consider the provider (AT\&T) as a seller. We also note that $\mcI_i$ is not the only
possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
minimal ordered subset where a
coordinated bid is possible, which we will address in further analysis in Section \ref{analysis}.
Suppose there exists buyer $k\in \mcI^j$, such that
$e_k^j(a) \ge e_i^j(a)
\rightarrow p_k^j > p_i^{j}$ and so $d^j - d_k^j < z_i^{j*}$, resulting in a
partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
set, (\ref{buyercoordinate}) states that $n$ is such that $e_i(a) = e_i^{j*}(a)
\ge e_k(a)$. We assume that $i$ will faithfully follow the opt-out strategy, and
so such a buyer $k$ cannot exist. 
Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$.

% BUYER LOCAL RESPONSE
{
\lemma{(Localized buyer response)}\label{buyerresponse}
As we cannot
assume that a buyers' bid will remain fixed at time $(t+1)$,
}\\
\textbf{Proof:} 
The first two cases, (\ref{partialallocation}) and (\ref{equalprice}) deal with
the problem of a buyer receiving a partial allocation:
In (\ref{partialallocation}), the winner with the lowest unit price $p_i^j$ results in a partial
allocation. In this case, using (\ref{buyercoordinate}), buyer $i$ will decrease its
quantity $d_i^j$ by increasing $n$, and will either remain a winner in $j$'s local
auction, or drop out of $\mcI^j$. (WILL USE LATER, DEVELOP MORE HERE?)
(\ref{equalprice}) considers that there may exist multiple buyers with the same unit price. The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
between all buyers with the same unit price. Therefore, again by
(\ref{buyercoordinate}), the buyers will increase $n$ until their demand is
met. 
The third case considers that a new buyer $k$ may enter the market with a better
price. There cannot be a buyer where $d_k^j > b^j$, as this violates
(\ref{budget}) imposed by (\ref{buyercoordinate}). When $d_k^j =
b^j$, the optimal solution at time $t$ is the single allocation, therefore at
time $(t+1)$, we have $\mcI^j = k$. It follows that in the case $d_k^j < b^j$, buyers $i\in\mcI^j$ will
lose their position in $\ell^j$ as the auction progresses and the minimal
subset $\mcI^j$ is computed. 
(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
Lastly, to resolve (\ref{emptyset}), $j$ chooses $n=I$, and sets its reserve price to $p_I^j$.

\subsubsection{Buyer Influence}
To determine a strategy for the sellers, we first perform a general examination
of seller incentive. The potential revenue for $j$ at unit price $y$ is determined by the
demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
\end{equation}
with ``inverse"
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
which it \emph{could} be sold to any buyer $i\in \mcI$ (as in \cite{semret}).
% SELLER VALUATION
We may now define the seller valuation (potential). 
{
\lemma{(Seller valuation)}\label{sellervaluation}
For any seller $j\in\mcI$, the contribution from buyer $i$'s valuation may be
modeled as,
\begin{equation}\label{singlevaluation}
    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
it follows that 
\begin{equation}\label{valuation}
    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a seller will try to maximize profit for any given allocation $a$, and
as such there is an incentive for $j$ to sell all of its data, and so 
$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = b^j =
\sum_{i\in\mcI} e_i$,
The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)

The sellers' natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
participate in any auction. We have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper.

As $j$ is restricted by
the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
{
% SELLER CONSTRAINTS
\lemma{(Seller constraints)}\label{constraints}
Let $j$ be a seller with budget $b^j$.
First, the seller must satisfy the quantity
constraint, 
\begin{equation}\label{quantity}
    d^j \ge e_i(a)
\end{equation}
and
\begin{equation}\label{budget}
    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j.
\end{equation}
In addition, for a rational seller, the reserve price must
satisfy 
\begin{equation}\label{reserveprice}
   p^j \ge \min_{i\in\mcI}\big({\theta_i}'(d_i^j)\big).
\end{equation}
}\\
\textbf{Proof:}
The first statement is an assumption, which we may enforce by (\ref{opt-out}),
and as a seller cannot sell more data than their bid, (\ref{budget}) enforces
the budget constraint for the seller. (\ref{reserveprice})
follows from the assumption that $j$ is rational, and so utility-maximization
acts as revenue maximization; a rational seller will not sell its
data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)

\subsubsection{Progressive User Strategy}
In order to to develop the seller strategy, it is necessary we determine 
that a seller has an incentive to
accept fractional bids (i.e. sell a fraction of their data $b^j$). Reasonably,
there may not exist a buyer such that $d_i = b^j$. In addition, a seller may accept
fractional bids in order to
maximize the revenue gained per unit of data by increasing market competition
\cite{???}.
Finally, in the case that the seller does not know the exact amount of
leftover data available, then they may only sell enough data to ensure that
they will not become a buyer while they submit their total data overage to the
secondary market. (FUTURE WORK? FROM \cite{zheng})

We describe the sellers' \emph{local} auction strategy for allocating its
data according to the constraints formed by the buyer strategy. As
local auction is progressive, and influenced by the $\epsilon$-best replies of
the buyers, we will need the following Lemma. (SHOULD I COUPLE THESE
ALGORITHMS? LESS OR MORE CONFUSING?)
We now define the local auction, which we describe, when coupled with the buyer
responses, as a progressive game of strategy with incomplete, but perfect
information (SAY MORE?).

% SELLER LOCAL STRATEGY
{
\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.

let the winner be determined by,
\begin{equation}\label{winner}
    \bar{i} = \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j.
\end{equation}
Also define
$$
    \ell^j =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
n}\sum_{i\in{\mcI}'} p_i^j,
$$
where,
\begin{equation}\label{sellercoordinate}
    n = \argmin_{\ell^j}(i \in \ell^j : \displaystyle\sum_{i\in\mcI^j} d_i^j >
b^j),
\end{equation} 
which gives $j$ a minimal subset 
\begin{equation}\label{buyers}
    \mcI^j = \lbrace i \in \mcI : i < n\rbrace \subset \mcI
\end{equation} 
of buyers that maximizes $j$'s revenue.
Define buyer $i^* = n \le I$ in the ordered set $\ell^j$.
Then, for time $(t+1)$, set $j$'s reserve price as 
\begin{equation}\label{newprice}
    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
\end{equation}
and update $j$'s budget to reflect the (tentative) allocation,
\begin{equation}\label{newbudget}
    \bar{b}^{j(t+1)} = b^{j(t)} - d_{i^*}^{j(t)}.
\end{equation}
Allowing $t$ to range over $\tau$, with buyer responses given as in Lemma
\ref{buyerresponse}, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
market equilibrium.% from time $t$ to $(t+1) \in \tau$.
}\\
\textbf{Proof:}
We will assume that the seller has enough data to satisfy at least one buyer,
in the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
price offer, determined by (\ref{sellercoordinate}). As the set of buyers is
computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
at equilibrium as it is designed so that the data offered by
seller $j$ equals the aggregate demand of the buyers \cite{???}
Although the buyers' valuation $\theta_i$ is not known to the seller, we assume
that the buyer is bidding truthfully, and so $p^j = {\theta_i}' + \epsilon
=p_i^j + \epsilon$, therefore $p^j$ is known, and as $\mcI^j\subset \mcI$, we
note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
(\ref{singlevaluation}), we have, $\forall \ z\ge 0$,
\begin{align*}
    \int_0^{e_{i^*}^{j}(a)} f^{j}(z)\ dz &\le\int_0^{e_i^{j}(a)}
f^{j}(z) \ dz 
\end{align*}
and so,
$$
    \theta^j\circ e_{i^*}(a) \le \theta^j\circ e_i(a),
$$
which holds $\forall \ i \in \mcI^j$.
It follows that, using
%, using (\ref{buyercoordinate}), 
the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
for any $\epsilon$-best reply, 
$$
    p^j \le {\theta_i}'(v_i^j) + \epsilon,
$$
$\forall i \in \mcI^j$.
Therefore the choice of $p^j$ does not force any buyers out of the local
equilibrium. Thus we determine the valuation between seller
$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
(NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK? SAVE
FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
